---
title: "Basic R Functions of Handling Financial Data"
author: "Zheng Tian"
output:
  pdf_document: default
  html_document: default
---

# Basic R Functions for Financial Data

## Downloading Financial Data

We can download financial data with the function `getSymbols()` in the package `quantmod` in R from open sources, like Yahoo Finance, Google Finance, and the Federal Reserve Bank of St. Louis (FRED).

```{r, results='hide'}
library(quantmod, quietly = TRUE)
options("getSymbols.warning4.0"=FALSE)
getSymbols('AAPL', src = "yahoo", from="2005-01-02", to="2010-12-31")
```

The data object obtained through `getSymbols()` is `xts`, i.e., extensible time series.
```{r}
class(AAPL)
```

We can check the data using `head()` and `tail`. And we can select a subset of the data within a range by calling the row names in the format as `yyyy-mm-dd`.

```{r}
# Look at the first three observations
head(AAPL, n = 3)

# Look at the observations from December 1st, 2010 to December 7th, 2010
AAPL["2010-12-01::2010-12-07"]
```


## Visualizing Financial Data

We can visualize the downloaded financial data with the function
`chartSeries()`.

```{r, fig.width=8, fig.height=5}
chartSeries(AAPL, subset = "2007::2009", theme = "white")
```

Since the data set comforms with an `OHLC` data format, we can plot the range of stock prices with a trading period with bar charts. In the following chart, we converted the daily stock prices to weekly prices using the function `to.weekly()`, and removed the trade volumn by setting `TA = NULL`.
```{r, fig.width=8, fig.height=5}
barChart(to.weekly(AAPL), subset = "2008:01::2009:01",
         theme='white.mono', TA = NULL, bar.type='ohlc')
```

Next we can generate the log return series, and plot it.
```{r, fig.width=8, fig.height=5}
aapl.rtn <- diff(log(AAPL))
chartSeries(aapl.rtn, subset = "2007::2009", type = 'line',
            TA = NULL, theme = "white")
```


# Linear Time Series Models with R

We consider the example of the monthly value-weighted return of IBM stock, which uses the data file `m-ibm3dx2608.txt`. 

```{r}
ibm_rtn <- read.table('m-ibm3dx2608.txt', header = TRUE)
head(ibm_rtn)
# tail(ibm_rtn)
```

We can convert the first column in `ibm_rtn` to a `Date` object, and convert the third column, which is the monthly value-weighted return, to a `ts` object. 

```{r}
ibm_date <- as.Date(as.character(ibm_rtn$date), "%Y%m%d")
class(ibm_date)
vw_rtn <- ts(ibm_rtn[, 3], start=c(1926, 1), frequency = 12)
```

We plot the series and its ACF and PACF. 
```{r, fig.align='center', fig.height=7}
op <- par(mfrow = c(3, 1), mar=c(3, 1, 3, 1), pty = "m")
plot(vw_rtn, main="The monthly value-weighted return of IBM stock")
acf_vw_rtn <- acf(vw_rtn, main="The ACF of the series")
pacf_vw_rtn <- pacf(vw_rtn, main="The PACF of the series")
par(op)
```

We use an AR(3) model to examine the return series, i.e.,

$$r_t  = \phi_0 + \phi_1 r_{t-1} + \phi_2 r_{t-2} + \phi_3 r_{t-3} + a_t$$

```{r}
vw_ar3 <- arima(vw_rtn, order=c(3,0,0))
vw_ar3
```

We can check the model adequacy by testing whether the residual series follows a white noise series. First, we plot the ACF of the residuals and then do a Ljung-Box test. 

```{r, fig.align="center", fig.height=6}
vw_ar3_resid <- resid(vw_ar3)
op <- par(mfrow = c(2, 1), mar=c(3, 1, 3, 1))
plot(vw_ar3_resid, main="The residuals from the AR(3) model")
acf(vw_ar3_resid, main="The ACF of residuals")
par(op)
```

The textbook suggest using the chi-squared distribution with the degree-of-freedom adjustment for the Ljung-Box statisitcs. 
```{r}
m <- 12
g <- length(coef(vw_ar3)) - 1
vw_ar3_lbtest <- Box.test(vw_ar3_resid, lag = m, type = "Ljung")
pv_ar3 <- 1 - pchisq(vw_ar3_lbtest$statistic, m-g)
```
The p-value is `r round(pv_ar3, 4)` greater than the 5% significant level so that we cannot reject the null hypothesis that the residuals are white noises, implying that the AR(3) model is adequate. 

Also, there is a function called `tsdiag` to check the residuals from a model estimation. 
```{r, fig.align='center', fig.height=7}
op <- par(mfrow = c(3, 1), mar=c(3, 1, 3, 1), pty = "m")
tsdiag(vw_ar3, 12)
par(op)
```


# Unit-Root Non-Stationarity

Finally, we demonstrate how to use R to examine a unit-root test with the example of the S&P 500 index.

```{r}
sp_data <- read.table("d-sp55008.txt", header=TRUE)
sp500 <- ts(log(sp_data[, 7]))
plot(sp500, main="The time series of S&P 500 index")
```

The series appears to be non-stationary and have a time trend. We can use the augmented Dickey-Fuller test to check the existence of unit-roots, and model the series with a time trend. 

```{r}
library(fUnitRoots, quietly = TRUE)

# Carry out the Dickey-Fuller test with a constant and time trend
adfTest(sp500, lags=2, type=("ct"))

# Model the series with time trend
dsp500 <- diff(sp500)
tdx <- 1:length(dsp500) 
m3 <- arima(dsp500, order=c(2,0,0), xreg=tdx)
m3
```

We then check the model adequacy with t statistics and the Ljung-Box test for the residuals. 

```{r, fig.align="center", fig.height=7}
# check the t statistics
tratio <- m3$coef / sqrt(diag(m3$var.coef))# compute t-ratio
tratio

# check the residuals
op <- par(mfrow = c(3, 1), mar=c(3, 1, 3, 1), pty = "m")
tsdiag(m3)
par(op)
```















